Discovery of barium stars in the LAMOST survey

### 2018-01-22 article/ms.tex
reorganise abstract

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Barium Stars in the Disk]{S-process Enhancement in Barium Disk Stars}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. Norfolk et al.]{
Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
Andrew R. Casey,$^{1,2}$
Mathew T. Miles,$^{1}$
Alex J. Kemp,$^{1}$ \newauthor
Karakas ? Lattanzio ? Schlaufman ? and others ?
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}
In this paper we present the analysis of 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements. Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses. Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star. Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model. We determined ... Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.

\end{abstract}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Barium stars in LAMOST]{Discovery of barium stars in the LAMOST survey}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
Andrew R. Casey,$^{1,2}$
Mathew T. Miles,$^{1}$
Alexander J. Kemp,$^{1}$ \newauthor
Karakas ? Lattanzio ? Schlaufman ? and others ?
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as Barium stars. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many barium stars have not evolved through the red giant (or main-sequence) phase and therefore cannot be an AGB star. These stars are generally thought to have accreted mass from a more evolved companion. For this reason the frequency and properties of less-evolved barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 257 barium stars from 454,180 giant stars observed by LAMOST. This sample constitutes the largest sample of barium stars discovered to date, and the most comprehensive search for barium stars in the Milky Way. \todo{Nearly all} of our barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.  
% Technitium?
\todo{Most (178/257) of our sample show strong carbon enhancement.}
Despite previous claims indicating that barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium. \todo{This implies ....}
 %Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses. Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star. Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model. 
% We determined ... Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.
\end{abstract}
